\chapter{Haar Measure}

\section{Reminder of General Topology}

\begin{definitionenv}[Open Mapping]\label{def:IsOpenMap}
    Let $X$ and $Y$ be topological spaces and $f: X\rightarrow Y$ be a mapping.
    We say that $f$ is an open mapping if for any open $U \subseteq X$, $f(U)$ is open in $Y$.
\end{definitionenv}

\begin{definitionenv}[Quotient Topology] % Mathlib uses coinduced topology to define this.
    Let $(X,\mathscr{T})$ be a topological space and $\pi : X\rightarrow Y$ be a surjective mapping.
    We call quotient topology of $\mathscr{T}$ on $Y$ (with respect to $\pi$) the family $V\subseteq Y$ such that 
    $\pi^{-1}(V) \in \mathscr{T}$.

    \quad Note that $\pi$ is continuous if we equipped $Y$ with the quotient topology.
\end{definitionenv}

\begin{propositionenv}
    Let $X,Y$ be topological spaces, $\pi : X\rightarrow Y$ be a surjective mapping.
    We equipped $Y$ with the quotient topology and assume that $\pi$ is open.
    \begin{enumerate}
        \item A subset $U$ of $Y$ is open if and only if $\pi^{-1}(U)$ is open in $X$.
        \item A subset $F$ of $Y$ is closed if and only if $\pi^{-1}(F)$ is closed in $X$.
    \end{enumerate}
\end{propositionenv}
\begin{proofenv}
    \quad 
    \begin{enumerate}
        \item $\pi$ is continuous, so if $U$ is open in $Y$, then $\pi^{-1}(U)$ is open in $X$.
        Conversely, if $\pi^{-1}(U)$ is open in $X$, then $\pi\left(\pi^{-1}(U)\right) = U$ is open.
        \item If $F$ is closed in $Y$, then $Y\setminus F$ is open, hence
        $X\setminus \pi^{-1}(F)=\pi^{-1}(Y\setminus F)$
        is open.
        Conversely, if $X\setminus \pi^{-1}(F)$ is open, then $\pi\left(\pi^{-1}\left(Y\setminus F\right)\right) = Y\setminus F$ is open.
    \end{enumerate}
\end{proofenv}
\begin{propositionenv}\label{prop:5.1.4}
    Let $I$ be a set, $\left(X_i\right)_{i\in I}$, $\left(Y_i\right)_{i\in I}$ be families of topological spaces.
    For any $i\in I$, let $f_i: X_i \rightarrow Y_i$ be a mapping.
    Let
    $$ X = \prod_{i\in I} X_i, \ Y = \prod_{i\in I} Y_i$$
    (Considered with initial topology) and let
    $$\begin{array}{rrcl}
        f : & X & \longrightarrow & Y\\
        & \left(x_i\right)_{i\in I} & \longmapsto & \left(f_i(x_i)\right)_{i\in I}.
    \end{array}$$

    \begin{enumerate}
        \item If $f_i$ is continuous for any $i\in I$, then $f$ is continuous.
        \item If $f_i$ is open for any $i\in I$ and is surjective for all but finitely many $i\in I$, then $f$ is open.
    \end{enumerate}
\end{propositionenv}
\begin{proofenv}
    \quad
    \begin{enumerate}
        \item For any $i\in I$, let $\pi_i : X\rightarrow X_i$, $p_i : Y \rightarrow Y_i$ be projections (all continuous).
            \begin{center}
                \begin{tikzcd}
                	X & Y \\
                	{X_i} & {Y_i}
                	\arrow["f", from=1-1, to=1-2]
                	\arrow["{\pi_i}"', from=1-1, to=2-1]
                	\arrow["{p_i}", from=1-2, to=2-2]
                	\arrow["{f_i}", from=2-1, to=2-2]
                \end{tikzcd}
                $$p_i \circ f = f_i \circ \pi_i$$
            \end{center}
            Since both $\pi_i$, $f_i$ are continuous so is $f_i \circ \pi_i$.
            Therefore $p_i \circ f$ is also continuous.
        \item Let $J_0$ be the set of $i\in I$ such that $f_i$ is not surjective.
            A topological basis of $X$ can be given by sets of the from
            $$ \bigcap_{j \in J} \pi_{j}^{-1} \left(U_j\right),$$
            where $J$ is a finite subset of $I$ containing $J_0$.
            Note that
            $$ f\left(\bigcap_{j \in J} \pi^{-1}_{j} (U_j)\right) = \bigcap_{j \in J} p^{-1}_{j}\left(f_j(U_j)\right).$$
            Since $f_j$ is open for any $j$, so must be $f$.
            (Checked on the basis of topology.)
    \end{enumerate}
\end{proofenv}

\begin{propositionenv}\label{thm:closure_pi_set}
    Let $I$ be a set and $(X_i)_{i\in I}$ be a family of topological spaces.
    Let $X$ be the product $(X_i)_{i\in I}$ with initial topology.
    For any $i\in I$, let $A_i \subseteq X_i$ and $C_i = \bar{A}_i$ (in $X_i$).
    Put $A = \prod_{i\in I}A_i$ and $C = \prod_{i\in I}C_i$,
    then
    $$ \bar{A} = C \text{ in } X.$$
\end{propositionenv}
\begin{proofenv}
    First, we prove that $C$ is closed in $X$.
    For any $i\in I$, let $\pi_i : X \rightarrow X_i$ be the projection to the $i$-th coordinate.
    We have
    $$ X\setminus C = \bigcup_{i \in I} \pi_i^{-1}\left(X_i \setminus C_i\right).$$
    For the remaining part, take $x = (x_i)_{i \in I}$ to be an element of $C$.
    We claim that for any open $U \ni x$, $U \cap A \neq \varnothing$
    \begin{center}
        

% Pattern Info
 
\tikzset{
pattern size/.store in=\mcSize, 
pattern size = 5pt,
pattern thickness/.store in=\mcThickness, 
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius, 
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_44loeb5b3}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_44loeb5b3}
{\pgfqpoint{0pt}{0pt}}
{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Regular Polygon [id:dp38747178348966016] 
\draw  [line width=2.25]  (312.77,150.33) .. controls (301.5,150.33) and (290.23,150.12) .. (278.96,150.33) .. controls (271.27,150.47) and (257.48,159.96) .. (251.91,164.63) .. controls (249.41,166.73) and (245.86,167.55) .. (243.8,170.08) .. controls (241.21,173.24) and (239.2,176.83) .. (237.03,180.3) .. controls (233.2,186.42) and (229.44,210.16) .. (237.71,215.71) .. controls (256.61,228.41) and (275.93,223.93) .. (297.22,226.61) .. controls (316.7,229.07) and (334.22,234.2) .. (354.02,232.74) .. controls (370.44,231.53) and (384.51,215.23) .. (386.48,199.37) .. controls (387.22,193.45) and (388.9,188.09) .. (385.13,183.02) .. controls (377.39,172.62) and (363.57,173.37) .. (352.67,170.08) .. controls (344,167.46) and (341.35,164.81) .. (336.44,159.86) .. controls (334.23,157.64) and (322.2,149.76) .. (312.77,150.33) -- cycle ;
%Shape: Circle [id:dp10118816507723016] 
\draw  [line width=2.25]  (270,147) .. controls (270,133.19) and (281.19,122) .. (295,122) .. controls (308.81,122) and (320,133.19) .. (320,147) .. controls (320,160.81) and (308.81,172) .. (295,172) .. controls (281.19,172) and (270,160.81) .. (270,147) -- cycle ;
%Shape: Free Drawing [id:dp7937280453890982] 
\draw  [line width=3] [line join = round][line cap = round] (296.74,148.73) .. controls (296.74,149.24) and (296.74,149.76) .. (296.74,150.27) ;
%Shape: Path Data [id:dp8272736758139742] 
\draw  [pattern=_44loeb5b3,pattern size=6pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 0; green, 0; blue, 0}][line width=2.25]  (312.77,150.33) .. controls (314.98,150.19) and (317.33,150.52) .. (319.66,151.13) .. controls (317.69,162.97) and (307.4,172) .. (295,172) .. controls (283.14,172) and (273.2,163.74) .. (270.64,152.65) .. controls (273.71,151.28) and (276.62,150.37) .. (278.96,150.33) .. controls (290.23,150.12) and (301.5,150.33) .. (312.77,150.33) -- cycle ;

% Text Node
\draw (288,185.4) node [anchor=north west][inner sep=0.75pt]    {$A$};
% Text Node
\draw (284,132.4) node [anchor=north west][inner sep=0.75pt]    {$x$};


\end{tikzpicture}
    \end{center}
    Without losing of generality, we can assume that $U = \prod_{i\in I}U_i$ such that for all $i\in I$ that $U_i$ open in $X_i$ and $U_i = X_i$ for all but finitely many $i \in I$
    ( $X = \prod_{i\in I}X_i $)
    Since $C_i = \bar{A}_i$, so $x_i \in U_i \cap A_i \neq \varnothing$ for any $i\in I$ hence
    $$ (x_i)_{i\in I} \in \prod_{i\in I} U_i \cap \prod_{i \in I}A_i = A.$$
    So $C$ is the closure of $A$.
\end{proofenv}

\begin{propositionenv}
    Let $X$ be a topological space and $\sim$ be an equivalence relation on $X$.
    Let $Y$ be the quotient of $X$ by equivalence relation considered with the quotient topology and let $\Gamma$ be the graph of $\sim$.
    \begin{enumerate}
        \item If $Y$ is Hausdorff, then $\Gamma$ is closed in $X \times X$.
         \item The converse is true if we assume that $\pi : X\rightarrow Y$ is open.
    \end{enumerate}
\end{propositionenv}
\begin{proofenv}
    Let
    $$ \Delta_Y \coloneq \{(y,y)\mid y \in Y\} \subseteq Y \times Y$$
    be the diagonal of $Y\times Y$.
    Consider
    $$\begin{array}{rrcl}
        \pi \times \pi : & X \times X & \longrightarrow & Y \times Y\\
        & \left(x_1,x_2\right) & \longmapsto & \left(\pi(x_1),\pi(x_2)\right).
    \end{array}$$
    By definition, $\Gamma = \left(\pi \times \pi\right)^{-1} \left(\Delta_Y\right)$, so if $Y$ is Hausdorff, then $\Gamma$ is closed, since $\pi \times \pi$ is continuous by 1. of \ref{prop:5.1.4}.

    \quad Assume that $\pi$ is open.
    By 2. of \ref{prop:5.1.4}, $\pi \times \pi$ is open.
    If $\Gamma$ is closed, then
    $$ X\times X \setminus \Gamma = \left(\pi \times \pi\right)^{-1} \left(Y \times Y \setminus \Delta_Y\right)$$
    is open.
    The image of this set by $\pi \times \pi$ identifies with $Y \times Y \setminus \Delta_Y$, so is also open.
    Hence $\Delta_Y$ is closed, i.e. $Y$ is Hausdorff.
\end{proofenv}

\begin{definitionenv}
    We say that a topological spaces $(X,\mathscr{T})$ is \textbf{disconnected} is there exists $U,V \subseteq X$ open and non-empty such that $U \cap V = \varnothing$ and $X = U \cup V$.
    If $X$ is not disconnected, then we say that it is \textbf{connected}.

    \quad We say that a subset $A \subseteq X$ is connected if $(A,\mathscr{T}|_A)$ is connected.
    
    \quad We say that $(X,\mathscr{T})$ is \textbf{path connected} if for any $x,y\in X$, there exists a continuous mapping $\gamma : [0,1]\rightarrow X$ such that $\gamma(0) = x$ and $\gamma(1) = y$.
\end{definitionenv}
\begin{propositionenv}\label{thm:connectedSpace_iff_clopen}
    Let $(X,\mathscr{T})$ be the topological space.
    $X$ is connected is and only if there does not exist a subset of $X$ different from both $X$ and $\varnothing$ that is simultaneously open and closed.
\end{propositionenv}
\begin{proofenv}
    Assume that there exists $U \subsetneq X$ such that $U \neq \varnothing$ and $U$ is simultaneously open and closed.
    Put $V = X\setminus U$, then $V \cap U = \varnothing$ and $V\cup U =X$, thus $X$ is disconnected, contradiction!
\end{proofenv}

\begin{exampleenv}
    $\sin\left(\frac{1}{x}\right) \cup \{(0,y): -1\le y\le 1\}$
 is connected but not path connected.
\end{exampleenv}

\begin{propositionenv}\label{thm:IsPathConnected.isConnected}
    Let $(X,\mathscr{T})$ be a topological space.
    If $X$ is path connected, then $X$ is connected.
\end{propositionenv}
\begin{proofenv}
    We write $X$ as the union of two disjoint non-empty subsets ($X = U\cup V,\ U\cap V =\varnothing,\ U,V \neq \varnothing$) that $X$ is disconnected but path connected.
    Pick $x\in U, y \in V$ and $\gamma:[0,1]\rightarrow X$ such that $\gamma(0) = x$ and $\gamma(1) = y$.
    Then $\gamma^{-1}(U)$, $\gamma^{-1}(V)$ are disjoint open subsets of $[0,1]$ containing $0$ and $1$ respectively and $[0,1] = \gamma^{-1}(U)\cup \gamma^{-1}(V)$.
    Let
    $$ a = \sup \{t \in [0,1] \mid \interval[open right]{0}{t} \subseteq \gamma^{-1}(U)\}.$$
    Since $\gamma^{-1}(U)$ is closed $a \in \gamma^{-1}(U)$.
    Since $\gamma^{-1}(U)$ is open, there exists $\varepsilon > 0$ such that $\interval[open]{a-\varepsilon}{a+\varepsilon} \subseteq \gamma^{-1}(U)$, contradiction!
\end{proofenv}

\begin{remark}
    Note that we proved that all intervals are connected.
\end{remark}

\begin{definitionenv}
    Let $(X,\mathscr{T})$ be a topological spaces.
    We call \textbf{connected component} of $X$ any non-empty maximal element of the set of all connected subsets of $X$ (equipped with the order of inclusion of sets).
    An empty topological space is connected but has no connected component.
\end{definitionenv}

\begin{lemmaenv}\label{thm:IsConnected.biUnion_of_reflTransGen}
    Let $(X,\mathscr{T})$ be a topological space, $\left(A_i\right)_{i\in I}$ family of non-empty connected subsets of $X$.
    If there exists $i_0 \in I$ such that for all $i \in I$, $A_{i} \cap A_{i_0} \neq \varnothing$, then $\bigcup_{i\in I}A_i$ is connected.
\end{lemmaenv}
\begin{proofenv}
    Suppose $U,V \subseteq X$, $U \cup V = X$, $U \cap V \neq \varnothing$,
    $$ \bigcup_{i\in I} A_i \subseteq U \cup V, \bigcup_{i\in I}A_i \cap \left(U \cap V\right) = \varnothing.$$
    $A_{i_0}$ is connected so $A_{i_0} \subseteq U$ or $A_{i_0} \subseteq V$.
    Without losing of generality, assume that $A_{i_0} \subseteq U$.
    For any $i \in I$, $\varnothing \neq A_i\cap A_{i_0} \subseteq A_{i_0} \subseteq U$.
    So for any $i \in I$, $A_i\cap U \neq \varnothing$, $A_i$ is connected $A_i \subseteq U$.
    Thus 
    $$ \bigcup_{i\in I}A_i \subseteq U.$$
\end{proofenv}

\begin{propositionenv}
    Let $(X,\mathscr{T})$ be a topological space.
    Then the following binary relation $\sim$ is an equivalence relation:
    \begin{center}
        $x \sim y \ \Leftrightarrow$ there exists a connected subset $A$ of $X$ such that $\{x,y\} \subseteq A$. 
    \end{center}
    Moreover, the equivalence classes of this relation are exactly the connected components of $(X,\mathscr{T})$.
    
    \quad In particular, any $x \in X$ belongs to a \textit{unique} connected component (called the \textbf{connected component} of $X$).
\end{propositionenv}
\begin{proofenv}
    $\sim$ is already reflexive and symmetric.
    We prove that $\sim$ is transitive.
    Let $x,y, z$ be elements of $X$ such that $\{x,y\}\subseteq A$ and $\{y,z\} \subseteq B$.
    One has $A \cap B \neq \varnothing$ case $y \in A \cap B$.
    So by lemma \ref{thm:IsConnected.biUnion_of_reflTransGen}, $A \cup B$ is connected and since ${x,z} \subseteq A \cup B$, one has $x \sim z$.

    \quad Let $C$ be a connected component of $X$ and $x \in X$.
    By definition, $x\sim y$ for any $y \in C$.
    If $z \in X$ is such that $x \sim Z$, then there exists connected $A \subseteq X$ such that $\{x,z\} \subseteq A$ and $A \cup C$ is connected.
    Since by definition, $C$ is maximal, we conclude that $A \subseteq C$ and $z \in C$, so $C$ is equal to the equivalence class of $x$.

    \quad Conversely, let $x \in X$ and $C$ be the equivalence class.
    By definition, any connected subset of $X$ containing $x$ must be contained in $C$.
    
    \quad It remains to check that $C$ is connected.
    
    \quad For any $y \in c$, there exists a connected set $A_y \supseteq \{x,y\}$.
    By lemma \ref{thm:IsConnected.biUnion_of_reflTransGen}, $\displaystyle \bigcup_{y \in C} A_y$ is connected and contains $C$.
    We conclude that
    $$C = \bigcup_{y \in C} A_y.$$
    Hence $C$ is connected.
\end{proofenv}

\begin{propositionenv}
    Let $(X,\mathscr{T})$ be a topological space.
    If $A \subseteq X$ is a connected subset of $X$, then $\bar{A}$ is also connected.
    In particular, any connected component of $X$ is closed.
\end{propositionenv}
\begin{proofenv}
    Suppose, by contradiction, that $U,V \subseteq X$ are open such that
    $$ (U \cap V) \cap \bar{A} = \varnothing,\ \bar{A} \subseteq U \cup V,\ U \cap \bar{A} \neq \varnothing,\ V \cap \bar{A} \neq \varnothing.$$
    But in this situation, one would also have $U \cap A \neq \varnothing$, $V \cap A \neq \varnothing$, $(U \cap V) \cap A =\varnothing$, $A \subseteq U \cup V$ which would contradict the assumption that $A$ is connected.
\end{proofenv}


\section{Topological Groups}

\begin{definitionenv}
    Let $(G,*)$ be a group with a topology $\mathscr{T}$.
    If the mapping
    $$\begin{array}{rrcl}
        \psi : & G\times G & \longrightarrow & G\\
        & (x,y) & \longmapsto & x*\iota(y)
    \end{array}$$
    is continuous, then we say that $(G,*,\mathscr{T})$ is a \textbf{topological group}.
\end{definitionenv}

\begin{definitionenv}
    Let $(G,*)$ be a group and $X$ be a set.
    Recall that a mapping $\varphi: G \times X \rightarrow X$ is called a left action (resp. right action) if the following conditions are satisfied
    \begin{enumerate}
        \item For any $x \in X$, $\varphi(e,x) = x$ ($e$ is the neutral element of $G$).
        \item For any $(a,b) \in G\times G$ and any $x \in X$,
            $$ \varphi(a*b, x) = \varphi(a,\varphi(b,x))\ (\text{resp. } \varphi(a*b, x) = \varphi(b,\varphi(a,x))).$$
    \end{enumerate}
    For any $a \in G$, we denote by $L_a : X \rightarrow X$ (resp. $R_a : X \rightarrow X$) the mapping sends any $x \in X$ to $\varphi(a,x)$.

    \quad If $(G,*,\mathscr{T})$ is a topological space, then we say that a left action (resp. right action) is continuous if $\varphi : G \times X \rightarrow X$ is continuous as a mapping when we consider $G \times X$ with the product topology.
\end{definitionenv}

\begin{propositionenv}\label{prop:5.2.3}
    Let $(G,*,\mathscr{T})$ be a topological group and $X$ be a topological space.
    Let $\varphi: G \times X \rightarrow X$ be a continuous left action (resp. right action) on $X$.
    Then for any $a \in G$, the mapping $L_a$ (resp. $R_a$) is a homeomorphism.
\end{propositionenv}
\begin{proofenv}
    We prove the left action case (right action case is similar).
    The mapping $L_a : X\rightarrow X$, $x \mapsto \varphi(a,x)$ can be written as the components
    $$ X \overset{i_a}{\longrightarrow} G \times X \overset{\varphi}{\longrightarrow} X$$
    where $i_a : X \rightarrow G\times X$ sends $x$ to $(a,x)$.
    Note that $i_a$ composed with the projections $G\times X \rightarrow G$ and $G \times X \rightarrow X$ give us a constant mapping and the identity on $X$ which are both continuous.
    Since projections are always continuous and open, we deduce that $i_a$ is continuous and hence also $L_a = i_a \circ \varphi$ is continuous.

    \quad By definition, 
    $$ L_a \circ L_{\iota(a)} = L_{\iota(a)} \circ L_{a} = \id_{X},$$
    we deduce that $L_a$ is a homeomorphism, cause $L_{\iota(a)}$ is continuous by the first half of the proof.
\end{proofenv}

\begin{propositionenv}
    Let $(G,*,\mathscr{T})$ be a topological group.
    \begin{enumerate}
        \item The inverse mapping $\iota : G\rightarrow G$ is a homeomorphism.
        \item $G \times G \rightarrow G$, $(a,b) \mapsto a*b$ is continuous and in particular, it defines a left action on $G$ in itself.
        \item $G \times G \rightarrow G$, $(a,b) \mapsto b*a$ is continuous and in particular, it defines a right action on $G$ in itself.
        \item For any $g \in G$,
            $$ L_g : G \rightarrow G, \ x \mapsto g*x,$$
            $$ R_g : G \rightarrow G, \ x \mapsto x*g,$$
            are homeomorphisms on $G$.
    \end{enumerate}
\end{propositionenv}
\begin{proofenv}
    Let $e \in G$ be the neutral element,
    and $p_1 : G \times G \rightarrow G$ and $p_2 : G \times G \rightarrow G$ be the two projections,
    namely $$ p_1(a,b) = a,\ p_2(a,b) = b.$$
    We note that $p_1$ and $p_2$ are both continuous and open.
    \begin{enumerate}
        \item The mapping $\lambda : G \rightarrow G \times G$, $x \mapsto (e,x)$ is continuous since its composite with each of the projections $p_1$ and $p_2$ is continuous.
            Therefore, the mapping $\iota : G \rightarrow G$, which is the composite 
            $$\begin{array}{ccccl}
                G & \overset{\lambda}{\longrightarrow} & G \times G & \overset{\varphi}{\longrightarrow} & G\\
                x & \longmapsto & (e,x) & \longmapsto & e* \iota(x)
            \end{array}$$
            is continuous.
            Since $\iota \circ \iota = \id_{G}$, we deduce that $\iota$ is a homeomorphism of $G$.
        \item Let $\tau : G \times G \rightarrow G \times G$, $(x,y) \mapsto (x, \iota(y))$ one has that $p_1 \circ \tau = p_1$, $p_2 \circ \tau = \iota \circ p_2$,
            and therefore $\tau$ is continuous.
            The mapping
            $$ \begin{array}{rrcl}
                G \times G \longrightarrow G\\
                (x,y) & \longmapsto & x*y
            \end{array}$$
            equals $\varphi \circ \tau$ so $(x,y) \mapsto x*y$ is continuous.
        \item $G \times G \rightarrow G \times G$, $(x,y) \mapsto (y,x)$ is continuous,
            since its composition with both $p_1$ and $p_2$ are continuous.
            The mapping $G \times G \rightarrow G$, $(x,y) \mapsto y*x$ is the composite of $(x,y) \mapsto (y,x)$ and $(x,y)\mapsto x*y$.
            Hence it si continuous.
        \item Follows from the proposition \ref{prop:5.2.3}.
    \end{enumerate}
\end{proofenv}

\begin{remark}
    Let $(G,*)$ be a group with topology $\mathscr{T}$.
    We can prove that $(G,*,\mathscr{T})$ is a topological group if and only if 
    $$\begin{array}{rrclcrrcl}
        \iota : & G & \longrightarrow & G & \quad & * : & G \times G & \longrightarrow & G \\
        & x & \longmapsto & \iota(x) & \quad & & (x,y) & \longmapsto & x*y
    \end{array}$$
    are both continuous.
\end{remark}

\begin{exampleenv}
    Let $(K, \left|\ \cdot\ \right|)$ be a valued field.
    The additive group $(K,+)$ is the multiplicative group $(K^\times,\cdot)$ are both topological groups.
\end{exampleenv}

\begin{exampleenv}
    Let $(K, \left|\ \cdot\ \right|)$ be a valued field, and $(V,\|\cdot\|)$ be a normed vector space over $K$.
    The additive group $(V,+)$ forms a topological group.
    Moreover, the mapping
    $$ \begin{array}{rrcl}
        K^\times \times V & \longrightarrow & V\\
        (a,x) & \longmapsto & ax
    \end{array}$$
    is a continuous left action.
\end{exampleenv}
